### 2016-03-10 paper5.tex
Made all references unique to its own paper/chapter.

\label{sec:intro}
There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits. In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}. Likewise, companions complicate direct imaging planet searches by requiring either extremely high-contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.

@@

In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{sec:method}. We describe the observations and data reduction in Section \ref{sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subsec:systematics} and the sensitivity of the method in Section \ref{subsec:sensitivity}. In Section \ref{sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{sec:conclusions}.

\section{Direct Spectral Detection Method}
\label{sec:method}

@@

\begin{equation}
w = \frac{v\sin{i} \cdot f}{c} \cdot \frac{\lambda_0}{\Delta \lambda}
\label{eqn:smoothing}
\end{equation}
where $v\sin{i}$ is the literature rotational velocity of the star, $\lambda_0$ is the central wavelength of the \'echelle order, $\Delta \lambda$ is the wavelength spacing per pixel of the order, $c$ is the speed of light, and $f = 0.25$ is an empirically determined parameter to give a visually adequate fit. Typical window sizes ranged from 50 - 100 pixels.

@@

\begin{itemize}
\item $T_\mathrm{eff} = 3000-7000$ K\footnote{We extend the grid to higher temperatures if the measured temperature (see Section \ref{subsec:systematics}) is near 7000 K}, in steps of 100 K
\item {[}Fe/H{]} = -0.5, 0.0, +0.5
\item $v\sin{i} = 1, 5, 10, 20, 30 \ \mathrm{km\ s}^{-1}$
\end{itemize}
Here, the $v\sin{i}$ is the rotational velocity of the secondary star. We account for the small influence that the smoothing kernel has on the companion spectrum by convolving the model with the same smoothing kernel used for the data, and subtracting the convolved model from the original. Treating the model spectrum in this way is more commonly known as unsharp masking. Finally, we cross-correlate every \'echelle order that does not have strong telluric residuals against the corresponding model spectrum, and combine the CCFs for each order using a simple average. The method is summarized below:

\begin{enumerate}
 \item Smooth the observed spectrum with a Gaussian smoothing kernel with width given by Equation \ref{eqn:smoothing}, and subtract the smoothed spectrum from the original
 \item Rotationally broaden the Phoenix model spectrum to the requested companion $v\sin{i}$
 \item Smooth the broadened spectrum to the instrumental resolution by convolving it with a gaussian kernel of appropriate width.
 \item Unsharp mask the broadened model spectrum
 \item Resample the processed model spectrum to the same wavelength spacing per pixel as the observed spectrum.
 \item Cross-correlate each \'echelle order against the corresponding processed model spectrum, and combine using a simple average.
\end{enumerate}

\section{Observations and Data Reduction}
\label{sec:obs}
We use three separate samples in this work. The first set, given in Table \ref{tab:earlycal}, contains  A- and B-type stars with the following published properties:

@@

The second dataset (Table \ref{tab:latecal}) contains F-M type stars which have a high-quality temperature estimate in the literature. We use the first two samples in Sections \ref{subsec:systematics} and \ref{subsec:sensitivity} to assess the accuracy of the temperature estimation using the DSD method and the sensitivity to companions of various temperatures.

Finally, we use the third dataset (Table \ref{tab:known}) to search for the spectral lines of the companion in several known binary systems. The third dataset has the same properties as the first, except that they have one \emph{and only one} known companion within $1 ''$. We further require that the literature data either puts no constraints on the companion temperature (as in the case of single-lined spectroscopic binaries) or that the companion has $T_\mathrm{eff} < 7500$ K.

We estimate the expected companion temperature depending on whether it is part of a spectroscopic (Table \ref{tab:specdata}) or visual (Table \ref{tab:imagedata}) binary system. In the case of double-lined spectroscopic binaries, we use the ratio of the semi-amplitudes given in the 9th catalog of spectroscopic binary orbits \citep[SB9,][]{SB9} to estimate the mass ratio of the system. We convert the primary star spectral type from the Simbad database \citep{Simbad} to mass by interpolating Table 5 of \citet{Pecaut2013}. The mass ratio and primary mass gives an estimate of the companion mass, which we convert to temperature by interpolating the same table. Most of the directly-imaged binary systems do not have orbital information, so we use the magnitude difference published in the Washington Double Star catalog \citep[WDS, ][]{WDS}. We use the Simbad spectral type of the primary star and Table 5 of \citet{Pecaut2013} to estimate the primary star temperature ($T_1$) and radius ($R_1$). We then find the companion temperature that minimizes the following function for the companion temperature ($T_2$), given the observed magnitude difference ($\Delta m_{obs}$)
\begin{equation}
Q = (m(T_2, R_2) - m(T_1, R_1) - \Delta m_{obs})^2
\label{eqn:secteff}
\end{equation}
where $m(T, R)$ is the Vega magnitude of a star with temperature T and radius R. We use the pysynphot package\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} and a Kurucz model grid \citep{Castelli2003} to calculate $m(T, R)$, and assume the companion is on the main sequence to estimate its radius ($R_2$). For both spectroscopic and visual binary systems, we assume spectral type uncertainties of $\pm 1$ subtype on the primary stars, and propagate the uncertainties into uncertainty in the companion temperature. We include the binary system in the sample if the expected companion temperature is $< 7500$ K.

@@

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{fig:error:a}
            \includegraphics[scale=0.45]{Figures/paper5_TS23_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[HRS]{
             \label{fig:error:b}
             \includegraphics[scale=0.45]{Figures/paper5_HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{fig:error:c}
             \includegraphics[scale=0.45]{Figures/paper5_IGRINS_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[CHIRON]{
             \label{fig:error:d}
             \includegraphics[scale=0.45]{Figures/paper5_CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectral detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subsec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{fig:error}
\end{figure}

\section{Parameter Determination}
\label{subsec:systematics}

@@

To measure the impact of both random and systematic noise on the parameter estimation, we created several hundred synthetic binary systems for each instrument used in our program. We made the synthetic binary systems by combining the early-type star spectra from Table \ref{tab:earlycal} with those of the late-type stars in Table \ref{tab:latecal} in every possible combination, provided both observations came from the same instrument. By combining actual observations of early-type and late-type stars, our synthetic binary observations retain any instrument-specific effects that may impact the temperature estimation. We scaled the flux of the late-type star such that the flux ratio ($F_\mathrm{secondary}/F_\mathrm{primary}$) is ten times larger than the expected flux ratio for main sequence components. The artificial brightening relative to a real binary system is to ensure that the temperature estimation uncertainties are separate from the overall sensitivity of the method, which we discuss in Section \ref{subsec:sensitivity}. We estimate the main sequence flux ratio from the published temperature of the late type star (given in Table \ref{tab:latecal}) and the published spectral types of the primaries available on Simbad \citep{Simbad}, and convert to temperature and luminosity by using Table 5 of \citet{Pecaut2013}.

@@

\begin{eqnarray}
\label{eqn:tmeas} 
T_m &=& \sum_i C_i T_i / \sum_i C_i \\
\sigma_T^2 &=& \frac{\sum_i C_i (T_i - T_m)^2}{ \sum_i C_i - \sum_i C_i^2 / \sum_i C_i}
\end{eqnarray}

Each synthetic binary observation contributes a pair of measured and actual (literature) companion temperatures, and so each late-type star in Table \ref{tab:latecal} has many independent temperature measurements made with the DSD method. To determine the correspondence between measured and actual temperature, we perform a Markov Chain Monte Carlo (MCMC) fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through

\begin{equation}
T_m = a + bT_a
\end{equation}
In Section \ref{sec:results} we invert this relation to determine the actual companion temperature, given the measured temperature from Equation \ref{eqn:tmeas}.

@@

\section{Detection Sensitivity}
\label{subsec:sensitivity}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper5_vsini_temperature_detection_rate_median.pdf}
  \caption{Median detection rate as a function of companion temperature and rotation speed. Each cell represents the median detection rate for targets with no detection in Table \ref{tab:known}. Companions represented by dark cells are detectable. See Section \ref{subsec:sensitivity} for details of the analysis.}
  \label{fig:sensitivity_2d}
\end{figure}

@@

The median detection rate for targets in Table \ref{tab:known} is shown in Figure \ref{fig:sensitivity_2d}\footnote{A file with the results of the sensitivity analysis, as well as sensitivity figures similar to Figure \ref{fig:sensitivity_2d} for each individual target, are available at this url: \url{https://github.com/kgullikson88/DSD-Paper}}. We can usually detect very cool stars if they are slowly rotating, but the sensitivity quickly degrades as the companion $v\sin{i}$ increases. Cool stars spin down as they age \citep{Barnes2003} so the rotation speed dependence is equivalent to an age dependence. We estimate the impact of rotation on our detection method by using the gyrochronology relation given in \cite{Barnes2010b}:

\begin{equation}
\frac{k_Ct}{\tau} = \ln\left ( \frac{P}{P_0} \right ) \frac{k_Ik_C}{2\tau^2} (P^2 - P_0^2)
\label{eqn:gyro}
\end{equation}

In Equation \ref{eqn:gyro}, $k_C$ and $k_I$ are constants fit to data with known ages and rotation periods, $P$ and $P_0$ are respectively the current and zero-age main sequence (ZAMS) rotation periods, $\tau$ is the convective turnover time scale and $t$ is the current age of the star. We use the same values that \cite{Barnes2010b} use for the constants:

@@

We use Equation \ref{eqn:gyro} to estimate the expected rotation period for a companion star of given temperature and age as follows: First, we convert from temperature to convective timescale ($\tau$) by interpolating Table 1 in \citet{Barnes2010a}. Next we sample an appropriate probability density function (PDF) for the age of the binary system; if the primary star was analyzed in \citet{David2015}, we use their posterior age PDFs. Otherwise, we use a uniform PDF from the Zero Age Main Sequence (ZAMS) age of the primary star to its main sequence lifetime (typically 10-200 Myr for our sample). Following the discussion in \cite{Barnes2010b}, we uniformly sample initial rotation periods from 0.2 - 5 days for all stars. We estimate the current rotation period for each pair of age and initial rotation period samples using Equation \ref{eqn:gyro} to build up a PDF of current rotation periods. We transform the period distribution into a PDF for $v\sin{i}$ using the main sequence radius of a star of the given temperature, obtained by interpolating Table 1 of \cite{Barnes2010a}, and a uniform sampling of inclinations ($\sin{i}$). Figure \ref{fig:vsini} shows a typical $v\sin{i}$ distribution, which peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and has a long tail extending to $\sim 40-50 \ \mathrm{km\ s}^{-1}$.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{Figures/paper5_vsini_PDF.pdf}
    \caption{Typical probability density function for companion rotational velocity $v\sin{i}$. The distribution peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and extends to very high velocities. Note that the x-axis is log-spaced to more clearly show the tails of the distribution.}
    \label{fig:vsini}
\end{figure}

By combining the sensitivity calculations described above with the $v\sin{i}$ samples, we marginalize over the expected rotation periods of the secondary stars to get simpler curves of detection rate as a function of companion star temperature. We show the median and approximate range of the marginalized detection rate in Figure \ref{fig:sensitivity}. The DSD method can reliably detect companions as cool as 3700 K in most cases, although the primary star spectral type plays a dominant role in setting the coolest detectable companion.

@@

         \caption{Summary of the detection rate as a function of temperature for the sample stars (Table \ref{tab:known}) in which we do not detect a companion. The red dashed line gives the median detection rate, and the blue filled area illustrates the range across different primary stars. The direct spectral detection method can detect companions as late as M0 for most of our targets.}
         \label{fig:sensitivity}
\end{figure}

\begin{figure*}
  \centering
  \subfigure[]{
       \label{fig:detections:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_13165+2013-08-14.pdf}
  }%
  \subfigure[]{
       \label{fig:detections:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2013-09-16.pdf}
  }

  \subfigure[]{
       \label{fig:detections:c}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2014-10-13.pdf}
  }%
  \subfigure[]{
       \label{fig:detections:d}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_24902+2014-10-16.pdf}
  }

  \subfigure[]{
       \label{fig:detections:e}
        \includegraphics[width= 75mm]{Figures/paper5_HIP_76267+2013-03-29.pdf}
  }

  \caption{Cross-correlation functions for detected companions}
  \label{fig:detections}
\end{figure*}

@@

  \subfigure[]{
       \label{fig:detections2:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_77516+2013-03-29.pdf}
  }%
   \subfigure[]{
       \label{fig:detections2:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79199+2014-03-18.pdf}
  }

  \subfigure[]{
       \label{fig:detections2:c}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79404+2013-05-03.pdf}
  }%
   \subfigure[]{
       \label{fig:detections2:d}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79404+2015-03-09.pdf}
  }

  \subfigure[]{
       \label{fig:detections2:e}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_84606+2014-10-15.pdf}
  }% 
  \subfigure[]{
       \label{fig:detections2:f}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_91118+2014-10-15.pdf}
  }

  \caption{Cross-correlation functions for detected companions}
  \label{fig:detections2}
\end{figure*}

\section{Application to Known Binary Systems}
\label{sec:results}

We now use the DSD method to measure the temperatures of several known binary systems (Table \ref{tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{sec:method}, and find the temperature of the companion using Equation \ref{eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subsec:systematics} (see also Figure \ref{fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

\begin{equation}
f = \int_{-\infty}^x {pdf(T)dT}
\end{equation}
We use as the central value the value of x such that $f=0.5$ (the median). Likewise, we calculate the $1 \sigma$ lower and upper bounds such that $f = 0.16$ and $f = 0.84$, respectively. The CCFs for the companions that we detect are shown in Figures \ref{fig:detections} and \ref{fig:detections2}. For each star, we show the CCF which has the maximum peak value and annotate the figures with the parameters. Most of the CCFs have very strong peaks. The exception is HIP 22958; however, the detection is strengthened by the fact that we observed this star twice and measured a similar temperature both times. The CCFs for HIP 22958 and HIP 24902 demonstrate the adverse effect a large companion rotational velocity has on the detection significance.

\subsection{Comparison to Literature Data}
\label{subsec:expected_teffs}
We use the literature data to predict an expected temperature for each companion in order to directly compare our measurements to previous results. The procedure outlined in Section \ref{sec:obs} using the magnitude difference or orbital information alone produces reasonable estimates, but in many cases there is additional information in the literature to refine the estimates. The refined estimates are described below.

@@

\citet{Zorec2012} find fundamental parameters for HIP 22958, and determine a temperature slightly cooler and luminosity much greater than the spectral type (B6V) would suggest. Because of this the usual analysis, which uses main sequence relationships, results in a biased answer. We estimate the companion temperature by assuming that the companion \emph{does} follow the main sequence relationships as described in Section \ref{sec:obs}, but sample the uncertainty distributions given in \citet{Zorec2012} for the temperature and radius of the primary star.

>>>>

\label{paper5_sec:intro}
There has recently been a revival of interest in the multiplicity properties of intermediate-mass stars,  spurred largely by the detection of planets orbiting nearby \mbox{$\sim2 M_{\odot}$} stars on both wide \citep[e.g.][]{Lagrange2010, Marois2008} and close \citep{Johnson2011} orbits. In this context, binary companions are contaminants; companions complicate radial velocity planet searches because they necessitate simultaneous modeling of both stellar motions \citep[e.g.][]{Bergmann2015}. Likewise, companions complicate direct imaging planet searches by requiring either extremely high-contrast instrumentation \citep{Thalmann2014} or specialized coronagraphs \citep{Crepp2010}.

@@

In this paper, we describe the DSD method in detail, and use it to detect the secondary star in nine known binary systems. We describe the method in Section \ref{paper5_sec:method}. We describe the observations and data reduction in Section \ref{paper5_sec:obs}, then use the observations to estimate the accuracy with which we can measure the companion temperature in Section \ref{subpaper5_sec:systematics} and the sensitivity of the method in Section \ref{subpaper5_sec:sensitivity}. In Section \ref{paper5_sec:results} we use the DSD method to search for known companions, and discuss the results in Section \ref{paper5_sec:conclusions}.

\section{Direct Spectral Detection Method}
\label{paper5_sec:method}

@@

\begin{equation}
w = \frac{v\sin{i} \cdot f}{c} \cdot \frac{\lambda_0}{\Delta \lambda}
\label{paper5_eqn:smoothing}
\end{equation}
where $v\sin{i}$ is the literature rotational velocity of the star, $\lambda_0$ is the central wavelength of the \'echelle order, $\Delta \lambda$ is the wavelength spacing per pixel of the order, $c$ is the speed of light, and $f = 0.25$ is an empirically determined parameter to give a visually adequate fit. Typical window sizes ranged from 50 - 100 pixels.

@@

\begin{itemize}
\item $T_\mathrm{eff} = 3000-7000$ K\footnote{We extend the grid to higher temperatures if the measured temperature (see Section \ref{subpaper5_sec:systematics}) is near 7000 K}, in steps of 100 K
\item {[}Fe/H{]} = -0.5, 0.0, +0.5
\item $v\sin{i} = 1, 5, 10, 20, 30 \ \mathrm{km\ s}^{-1}$
\end{itemize}
Here, the $v\sin{i}$ is the rotational velocity of the secondary star. We account for the small influence that the smoothing kernel has on the companion spectrum by convolving the model with the same smoothing kernel used for the data, and subtracting the convolved model from the original. Treating the model spectrum in this way is more commonly known as unsharp masking. Finally, we cross-correlate every \'echelle order that does not have strong telluric residuals against the corresponding model spectrum, and combine the CCFs for each order using a simple average. The method is summarized below:

\begin{enumerate}
 \item Smooth the observed spectrum with a Gaussian smoothing kernel with width given by Equation \ref{paper5_eqn:smoothing}, and subtract the smoothed spectrum from the original
 \item Rotationally broaden the Phoenix model spectrum to the requested companion $v\sin{i}$
 \item Smooth the broadened spectrum to the instrumental resolution by convolving it with a gaussian kernel of appropriate width.
 \item Unsharp mask the broadened model spectrum
 \item Resample the processed model spectrum to the same wavelength spacing per pixel as the observed spectrum.
 \item Cross-correlate each \'echelle order against the corresponding processed model spectrum, and combine using a simple average.
\end{enumerate}

\section{Observations and Data Reduction}
\label{paper5_sec:obs}
We use three separate samples in this work. The first set, given in Table \ref{paper5_tab:earlycal}, contains  A- and B-type stars with the following published properties:

@@

The second dataset (Table \ref{paper5_tab:latecal}) contains F-M type stars which have a high-quality temperature estimate in the literature. We use the first two samples in Sections \ref{subpaper5_sec:systematics} and \ref{subpaper5_sec:sensitivity} to assess the accuracy of the temperature estimation using the DSD method and the sensitivity to companions of various temperatures.

Finally, we use the third dataset (Table \ref{paper5_tab:known}) to search for the spectral lines of the companion in several known binary systems. The third dataset has the same properties as the first, except that they have one \emph{and only one} known companion within $1 ''$. We further require that the literature data either puts no constraints on the companion temperature (as in the case of single-lined spectroscopic binaries) or that the companion has $T_\mathrm{eff} < 7500$ K.

We estimate the expected companion temperature depending on whether it is part of a spectroscopic (Table \ref{paper5_tab:specdata}) or visual (Table \ref{paper5_tab:imagedata}) binary system. In the case of double-lined spectroscopic binaries, we use the ratio of the semi-amplitudes given in the 9th catalog of spectroscopic binary orbits \citep[SB9,][]{SB9} to estimate the mass ratio of the system. We convert the primary star spectral type from the Simbad database \citep{Simbad} to mass by interpolating Table 5 of \citet{Pecaut2013}. The mass ratio and primary mass gives an estimate of the companion mass, which we convert to temperature by interpolating the same table. Most of the directly-imaged binary systems do not have orbital information, so we use the magnitude difference published in the Washington Double Star catalog \citep[WDS, ][]{WDS}. We use the Simbad spectral type of the primary star and Table 5 of \citet{Pecaut2013} to estimate the primary star temperature ($T_1$) and radius ($R_1$). We then find the companion temperature that minimizes the following function for the companion temperature ($T_2$), given the observed magnitude difference ($\Delta m_{obs}$)
\begin{equation}
Q = (m(T_2, R_2) - m(T_1, R_1) - \Delta m_{obs})^2
\label{paper5_eqn:secteff}
\end{equation}
where $m(T, R)$ is the Vega magnitude of a star with temperature T and radius R. We use the pysynphot package\footnote{pysynphot is a python code package to perform synthetic photometry, and is available at this url: \url{https://pypi.python.org/pypi/pysynphot}} and a Kurucz model grid \citep{Castelli2003} to calculate $m(T, R)$, and assume the companion is on the main sequence to estimate its radius ($R_2$). For both spectroscopic and visual binary systems, we assume spectral type uncertainties of $\pm 1$ subtype on the primary stars, and propagate the uncertainties into uncertainty in the companion temperature. We include the binary system in the sample if the expected companion temperature is $< 7500$ K.

@@

\begin{figure}
        \centering
        \subfigure[TS23]{
            \label{paper5_fig:error:a}
            \includegraphics[scale=0.45]{Figures/paper5_TS23_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[HRS]{
             \label{paper5_fig:error:b}
             \includegraphics[scale=0.45]{Figures/paper5_HET_simple_Tact2Tmeas.pdf}
         }
         \subfigure[IGRINS]{
             \label{paper5_fig:error:c}
             \includegraphics[scale=0.45]{Figures/paper5_IGRINS_simple_Tact2Tmeas.pdf}
         }%
         \subfigure[CHIRON]{
             \label{paper5_fig:error:d}
             \includegraphics[scale=0.45]{Figures/paper5_CHIRON_simple_Tact2Tmeas.pdf}
         }
         \caption{Correspondence between the companion temperature measured with the direct spectral detection method, and the actual (literature) values. In all figures, the red dashed line has unity slope, the values with uncertainties are the measurements from the synthetic binary observations (see Section \ref{subpaper5_sec:systematics}), and the blue lines are the line of best-fit through the data. There is significant bias in all of the measurements except for those using the near-infrared IGRINS instrument.}
         \label{paper5_fig:error}
\end{figure}

\section{Parameter Determination}
\label{subpaper5_sec:systematics}

@@

To measure the impact of both random and systematic noise on the parameter estimation, we created several hundred synthetic binary systems for each instrument used in our program. We made the synthetic binary systems by combining the early-type star spectra from Table \ref{paper5_tab:earlycal} with those of the late-type stars in Table \ref{paper5_tab:latecal} in every possible combination, provided both observations came from the same instrument. By combining actual observations of early-type and late-type stars, our synthetic binary observations retain any instrument-specific effects that may impact the temperature estimation. We scaled the flux of the late-type star such that the flux ratio ($F_\mathrm{secondary}/F_\mathrm{primary}$) is ten times larger than the expected flux ratio for main sequence components. The artificial brightening relative to a real binary system is to ensure that the temperature estimation uncertainties are separate from the overall sensitivity of the method, which we discuss in Section \ref{subpaper5_sec:sensitivity}. We estimate the main sequence flux ratio from the published temperature of the late type star (given in Table \ref{paper5_tab:latecal}) and the published spectral types of the primaries available on Simbad \citep{Simbad}, and convert to temperature and luminosity by using Table 5 of \citet{Pecaut2013}.

@@

\begin{eqnarray}
\label{paper5_eqn:tmeas} 
T_m &=& \sum_i C_i T_i / \sum_i C_i \\
\sigma_T^2 &=& \frac{\sum_i C_i (T_i - T_m)^2}{ \sum_i C_i - \sum_i C_i^2 / \sum_i C_i}
\end{eqnarray}

Each synthetic binary observation contributes a pair of measured and actual (literature) companion temperatures, and so each late-type star in Table \ref{paper5_tab:latecal} has many independent temperature measurements made with the DSD method. To determine the correspondence between measured and actual temperature, we perform a Markov Chain Monte Carlo (MCMC) fit to a straight line using the emcee code \citep{emcee}. We plot the mean and standard deviation of the measured temperatures in Figure \ref{paper5_fig:error}, along with 300 MCMC samples for the linear fit and the line of unity slope. The MCMC samples give posterior probability distributions for the parameters $a$ and $b$ relating the actual temperature ($T_a$) to the measured temperature ($T_m$) through

\begin{equation}
T_m = a + bT_a
\end{equation}
In Section \ref{paper5_sec:results} we invert this relation to determine the actual companion temperature, given the measured temperature from Equation \ref{paper5_eqn:tmeas}.

@@

\section{Detection Sensitivity}
\label{subpaper5_sec:sensitivity}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Figures/paper5_vsini_temperature_detection_rate_median.pdf}
  \caption{Median detection rate as a function of companion temperature and rotation speed. Each cell represents the median detection rate for targets with no detection in Table \ref{paper5_tab:known}. Companions represented by dark cells are detectable. See Section \ref{subpaper5_sec:sensitivity} for details of the analysis.}
  \label{paper5_fig:sensitivity_2d}
\end{figure}

@@

The median detection rate for targets in Table \ref{paper5_tab:known} is shown in Figure \ref{paper5_fig:sensitivity_2d}\footnote{A file with the results of the sensitivity analysis, as well as sensitivity figures similar to Figure \ref{paper5_fig:sensitivity_2d} for each individual target, are available at this url: \url{https://github.com/kgullikson88/DSD-Paper}}. We can usually detect very cool stars if they are slowly rotating, but the sensitivity quickly degrades as the companion $v\sin{i}$ increases. Cool stars spin down as they age \citep{Barnes2003} so the rotation speed dependence is equivalent to an age dependence. We estimate the impact of rotation on our detection method by using the gyrochronology relation given in \cite{Barnes2010b}:

\begin{equation}
\frac{k_Ct}{\tau} = \ln\left ( \frac{P}{P_0} \right ) \frac{k_Ik_C}{2\tau^2} (P^2 - P_0^2)
\label{paper5_eqn:gyro}
\end{equation}

In Equation \ref{paper5_eqn:gyro}, $k_C$ and $k_I$ are constants fit to data with known ages and rotation periods, $P$ and $P_0$ are respectively the current and zero-age main sequence (ZAMS) rotation periods, $\tau$ is the convective turnover time scale and $t$ is the current age of the star. We use the same values that \cite{Barnes2010b} use for the constants:

@@

We use Equation \ref{paper5_eqn:gyro} to estimate the expected rotation period for a companion star of given temperature and age as follows: First, we convert from temperature to convective timescale ($\tau$) by interpolating Table 1 in \citet{Barnes2010a}. Next we sample an appropriate probability density function (PDF) for the age of the binary system; if the primary star was analyzed in \citet{David2015}, we use their posterior age PDFs. Otherwise, we use a uniform PDF from the Zero Age Main Sequence (ZAMS) age of the primary star to its main sequence lifetime (typically 10-200 Myr for our sample). Following the discussion in \cite{Barnes2010b}, we uniformly sample initial rotation periods from 0.2 - 5 days for all stars. We estimate the current rotation period for each pair of age and initial rotation period samples using Equation \ref{paper5_eqn:gyro} to build up a PDF of current rotation periods. We transform the period distribution into a PDF for $v\sin{i}$ using the main sequence radius of a star of the given temperature, obtained by interpolating Table 1 of \cite{Barnes2010a}, and a uniform sampling of inclinations ($\sin{i}$). Figure \ref{paper5_fig:vsini} shows a typical $v\sin{i}$ distribution, which peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and has a long tail extending to $\sim 40-50 \ \mathrm{km\ s}^{-1}$.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{Figures/paper5_vsini_PDF.pdf}
    \caption{Typical probability density function for companion rotational velocity $v\sin{i}$. The distribution peaks near $\sim 5-10$ $\mathrm{km\ s}^{-1}$ and extends to very high velocities. Note that the x-axis is log-spaced to more clearly show the tails of the distribution.}
    \label{paper5_fig:vsini}
\end{figure}

By combining the sensitivity calculations described above with the $v\sin{i}$ samples, we marginalize over the expected rotation periods of the secondary stars to get simpler curves of detection rate as a function of companion star temperature. We show the median and approximate range of the marginalized detection rate in Figure \ref{paper5_fig:sensitivity}. The DSD method can reliably detect companions as cool as 3700 K in most cases, although the primary star spectral type plays a dominant role in setting the coolest detectable companion.

@@

         \caption{Summary of the detection rate as a function of temperature for the sample stars (Table \ref{paper5_tab:known}) in which we do not detect a companion. The red dashed line gives the median detection rate, and the blue filled area illustrates the range across different primary stars. The direct spectral detection method can detect companions as late as M0 for most of our targets.}
         \label{paper5_fig:sensitivity}
\end{figure}

\begin{figure*}
  \centering
  \subfigure[]{
       \label{paper5_fig:detections:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_13165+2013-08-14.pdf}
  }%
  \subfigure[]{
       \label{paper5_fig:detections:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2013-09-16.pdf}
  }

  \subfigure[]{
       \label{paper5_fig:detections:c}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_22958+2014-10-13.pdf}
  }%
  \subfigure[]{
       \label{paper5_fig:detections:d}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_24902+2014-10-16.pdf}
  }

  \subfigure[]{
       \label{paper5_fig:detections:e}
        \includegraphics[width= 75mm]{Figures/paper5_HIP_76267+2013-03-29.pdf}
  }

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections}
\end{figure*}

@@

  \subfigure[]{
       \label{paper5_fig:detections2:a}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_77516+2013-03-29.pdf}
  }%
   \subfigure[]{
       \label{paper5_fig:detections2:b}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79199+2014-03-18.pdf}
  }

  \subfigure[]{
       \label{paper5_fig:detections2:c}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79404+2013-05-03.pdf}
  }%
   \subfigure[]{
       \label{paper5_fig:detections2:d}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_79404+2015-03-09.pdf}
  }

  \subfigure[]{
       \label{paper5_fig:detections2:e}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_84606+2014-10-15.pdf}
  }% 
  \subfigure[]{
       \label{paper5_fig:detections2:f}
       \includegraphics[width= 75mm]{Figures/paper5_HIP_91118+2014-10-15.pdf}
  }

  \caption{Cross-correlation functions for detected companions}
  \label{paper5_fig:detections2}
\end{figure*}

\section{Application to Known Binary Systems}
\label{paper5_sec:results}

We now use the DSD method to measure the temperatures of several known binary systems (Table \ref{paper5_tab:known}). We cross-correlate the spectra against the full grid of model spectra enumerated in Section \ref{paper5_sec:method}, and find the temperature of the companion using Equation \ref{paper5_eqn:tmeas}. We then convert the measured temperature to PDFs of the true companion temperature using the MCMC chains developed in Section \ref{subpaper5_sec:systematics} (see also Figure \ref{paper5_fig:error}). For stars with multiple observations, we multiply the PDFs from each detection. Finally, we calculate the companion temperature and confidence interval from the integral of the PDF:

\begin{equation}
f = \int_{-\infty}^x {pdf(T)dT}
\end{equation}
We use as the central value the value of x such that $f=0.5$ (the median). Likewise, we calculate the $1 \sigma$ lower and upper bounds such that $f = 0.16$ and $f = 0.84$, respectively. The CCFs for the companions that we detect are shown in Figures \ref{paper5_fig:detections} and \ref{paper5_fig:detections2}. For each star, we show the CCF which has the maximum peak value and annotate the figures with the parameters. Most of the CCFs have very strong peaks. The exception is HIP 22958; however, the detection is strengthened by the fact that we observed this star twice and measured a similar temperature both times. The CCFs for HIP 22958 and HIP 24902 demonstrate the adverse effect a large companion rotational velocity has on the detection significance.

\subsection{Comparison to Literature Data}
\label{subpaper5_sec:expected_teffs}
We use the literature data to predict an expected temperature for each companion in order to directly compare our measurements to previous results. The procedure outlined in Section \ref{paper5_sec:obs} using the magnitude difference or orbital information alone produces reasonable estimates, but in many cases there is additional information in the literature to refine the estimates. The refined estimates are described below.

@@

\citet{Zorec2012} find fundamental parameters for HIP 22958, and determine a temperature slightly cooler and luminosity much greater than the spectral type (B6V) would suggest. Because of this the usual analysis, which uses main sequence relationships, results in a biased answer. We estimate the companion temperature by assuming that the companion \emph{does} follow the main sequence relationships as described in Section \ref{paper5_sec:obs}, but sample the uncertainty distributions given in \citet{Zorec2012} for the temperature and radius of the primary star.
